---
title: "Module 3 CT Option 2"
author: "Shaun Stearns"
date: "8/2/2019"
output: word_document
---

#Load Required Packages
```{r}
library(rpart)
library(rpart.plot)
library(caret)
library(randomForest)
library(adabag)
library(jtools)
library(sandwich)
```

#Set Working Directory and read csv file
```{r}
Toyota.ct <- read.csv("ToyotaCorolla.csv")
```

#Dimension of the frame
```{r}
dim(Toyota.ct) 
```

#First six rows
```{r}
head(Toyota.ct) 
```

#Print a list of variables as a refernce guide
```{r}
t(t(names(Toyota.ct)))
```

#Subset of predictors requested by the shareholder
```{r}
Toyota.ct <- Toyota.ct[c(3,4,7,8,9,12,14,17,19,21,25,26,28,30,34,39)]
```

#Summary Statistics for each varaible
```{r}
summary(Toyota.ct)
```

#Check for Missing values
###No missing values were found
```{r}
data.frame(miss.val=sapply(Toyota.ct, function(x) 
  sum(length(which(is.na(x))))))
```

#Multiple Regression 
###Run to see if any variables can be eliminated, partial and part coefficients added to understand how much variability is accounted for by each variable. Jtools was used to provide a more comrpehensive regression analysis.
```{r}
ToyReg <- lm(Price~ ., data = Toyota.ct)
summ(ToyReg, scale = TRUE, part.corr = TRUE, digits = 3)
```

#Default Regression Tree
###Provides a preview of the most relevant variables predicting Price.
```{r}
ToyReg.tree <- rpart(Price ~ ., data = Toyota.ct, method = "anova")
length(ToyReg.tree$frame$var[ToyReg.tree$frame$var == "<leaf>"])
prp(ToyReg.tree, type = 1, extra = 1, under = TRUE, split.font = 1, varlen = -10, digits=-6)
```

#Deep Regression Tree 
###At 121 leafs, I chose not to produce this tree due to technical limitations.
```{r}
ToyReg.tree <- rpart(Price ~ ., data = Toyota.ct, method = "anova", cp = 0, maxdepth = 30)
length(ToyReg.tree$frame$var[ToyReg.tree$frame$var == "<leaf>"])
```

#Specified Regression Tree 
###This tree specifically meets the parameters requested by the share holder.
```{r}
ToyReg.tree <- rpart(Price ~ ., data = Toyota.ct, method = "anova", cp = 0.001, maxdepth = 30)
length(ToyReg.tree$frame$var[ToyReg.tree$frame$var == "<leaf>"])
prp(ToyReg.tree, type = 1, extra = 1, under = TRUE, split.font = 1, varlen = -10, digits=-6)
```

#Pruned Regression Tree: Best pruned regression tree. 
###It's interesting that there are more leaves produced than the code requested by the shareholder.
```{r}
Toy.ct <- rpart(Price ~ ., data = Toyota.ct, method = "anova",
                cp = 0.001, minsplit = 5, xval = 5)
length(ToyReg.tree$frame$var[ToyReg.tree$frame$var == "<leaf>"])
printcp(Toy.ct)

pruned.ct <- prune(Toy.ct,
                   cp = Toy.ct$cptable[which.min(Toy.ct$cptable[,"xerror"]), "CP"])
length(pruned.ct$frame$var[pruned.ct$frame$var == "<leaf>"])
prp(pruned.ct, type = 1, extra = 1, split.font = 1, varlen = -10, digits=-6)
```